---
title: "dynet"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dynet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dynet)
```

# Ising Glauber #
  In the Ising-Glauber model, each node has a binary state. At every
        time step, nodes switch their state with certain probability. For
        inactive nodes, this probability is 
        $\frac{1}{1+e^{\beta(k - 2m)/k}}$
   where is a parameter tuning the likelihood
        of switching state, $k$ is degree of the node and $m$
        is the number of its active neighbors; for active nodes the
        switch-state probability is $1-\frac{1}{1+e^{\beta(k-2m)/k}}$ instead.
        
      
## Params ##
* **input_matrix** The input (ground-truth) adjacency matrix of a graph with $N$ nodes. Must be valid square adjacency matrix.
* **L** Integer length of the desired time series.#
* **init** Vector initial condition, which must have binary value ($0$ or $1$).
* **beta** Float  Inverse temperature tuning the likelihood that a node switches its state. Default to $2$.

## Returns ##
* An $N\times L$ observations on N nodes.
    
## Code Example ##
```{r}
input <- matrix(
    cbind(
        c(1.0, 1.0, 2.0, 3.0),
        c(0.0, 0.0, 1.0, 0.0),
        c(0.0, 0.0, 0.0, 1.0),
        c(0.0, 0.0, 0.0, 0.0)
    ),
    nrow = 4
)
dynet::simulate_ising(input, L = 3, init = NULL, beta = 2)
dynet::simulate_ising(input, L = 3, init = c(1, 2, 3, 4), beta = 4)
```

# Kuramoto #
Simulate Kuramoto model on a ground truth network.
        Kuramoto oscillators model synchronization processes. At each time
        step, each node adjusts its phase $\theta_i$ according to the
        equation
        $\theta_i=\omega_i + \frac{\lambda}{N}\sum_{j=1}^{N}\sin\left(\theta_j - \theta_i\right)$
 where $\lambda$, is a coupling $strength$ parameter and each node
        has an internal frequency $\omega_i$; the $freqs$ function
        parameter provides the option to initialize these frequencies with
        user-defined values (or leave as $NULL$ to randomly initialize). Each
        node's initial phase $\theta_{i0}$ can be randomly initialized
        (the default behavior) or set by specifying the `phases` parameter.
        The results list also stores the ground truth network as
        $groundtruth$ and the internal frequencies of the process as
        $internalfrequencies$
        
## Params ##
* **input_matrix** The input (ground-truth) adjacency matrix of a graph with $N$ nodes. Must be valid square adjacency matrix.
* **L** Integer length of the desired time series.
* **dt** Float size of timestep for numerical integration.
* **strength** Float coupling strength (prefactor for interaction terms).
* **phases** Vector of of initial phases.
* **freqs** Vector of internal frequencies.

## Returns ##
* An $N\times L$ matrix of synthetic time series data.
    
## Code Example ##
```{r}
input <- matrix(
  cbind(
    c(1,0,0),
    c(0,1,0),
    c(0,1,0)
  ),
  ncol = 3
)
dynet::simulate_kuramoto(input, 3, dt = 1, strength = 1, phases = c(1,2,3), freqs = c(1.0, 1.05,1.06))
dynet::simulate_kuramoto(input, 3)
```

# Lotka-Volterra #
Simulate time series on a network from the Lotka-Volterra model.
        The Lotka-Volterra model was designed to describe dynamics of
        species abundances in an ecosystem. Species $i$s abundance
        change per time is $\frac{dX_i}{d t}=r_iX_i(1-\frac{X_i}{K_i}+\sum_{j\neq i}W_{ij}\frac{X_j}{K_i})$
        where $r_i$ and $K_i$ are the growth rate and the
        carrying capacity of species $i$respectively, and
        :math:$W_{ij}$ are the relative interaction strength of species
        $j$ on $i$.
        The results dictionary also stores the ground truth network as
        $groundtruth$ and the intermediate time steps as $timesteps$.
        
## Params ##
* **input_matrix** The input (ground-truth) adjacency matrix of a graph with $N$ nodes. Must be valid square adjacency matrix.
* **L** Integer length of the desired time series.
* **init** Initial condition vector. If not specified an initial condition is uniformly generated from 0 to the nodes' carrying capacity.
* **gr** Growth rate vector. If not specified, default to 1 for all nodes.
* **cap** Carrying capacity vector. If not specified, default to 1 for all nodes.
* **inter** $N\times N$ Matrix of interaction weights between nodes. If not specified, default to a zero-diagonal matrix whose ${i,j}$ entry is $(j - i)/(N-1)$
* **dt** Float or vector of sizes of time steps when simulating the continuous-time dynamics.
* **stochastic** Boolean determining whether to simulate the stochastic or deterministic dynamics.
* **pertb** Vector of perturbation magnitude of nodes' growth. If not specified, default to 0.01 for all nodes.

## Returns ##
* An $N\times L$ matrix of synthetic time series data.
    
## Code Example ##
```{r}
input <- matrix(
  cbind(
    c(1,0,0),
    c(0,1,0),
    c(0,1,0)
  ),
  ncol = 3
)
dynet::simulate_lotka(input, L = 3, init = c(0.9662720, 0.7750888, 0.9066647), dt = c(5,3,1))
dynet::simulate_sherrington(input, 10)
```

# Sherrington-Kirkpatrick #
Simulate Kinetic Ising model dynamics on a ground truth network.
        The results dictionary also stores the ground truth network as
        $groundtruth$.
        
## Params ##
* **input_matrix** The input (ground-truth) adjacency matrix of a graph with $N$ nodes. Must be valid square adjacency matrix.
* **L** Integer length of the desired time series.
* **noise** TRUE or FALSE value to generate noise

## Returns ##
* An $N\times L$ matrix of synthetic time series data.
    
## Code Example ##
```{r}
input <- matrix(
  cbind(
    c(1.0, 1.0, 2.0, 3.0),
    c(0.0, 0.0, 1.0, 0.0),
    c(0.0, 0.0, 0.0, 1.0),
    c(0.0, 0.0, 0.0, 0.0)
  ),
  nrow = 4
)
dynet::simulate_sherrington(input, 5, noise = TRUE)
dynet::simulate_sherrington(input, 10)
```

# Single Unbaised Random Walker #
Simulate single random-walker dynamics on a ground truth network.
        Generates an $N\times L$ time series $TS$ with
        $TS[j,t]==1$ if the walker is at node $j$ at time
        $t$, and $TS[j,t]==0$ otherwise.
        The results dictionary also stores the ground truth network as
        $groundtruth$.
        
## Params ##
* **input_matrix** The input (ground-truth) adjacency matrix of a graph with $N$ nodes. Must be valid square adjacency matrix.
* **L** Integer length of the desired time series.
* **initial_node** Starting node for walk

## Returns ##
* An $N\times L$ matrix of synthetic time series data.
    
## Code Example ##
```{r}
input <- matrix(
  cbind(
    c(1, 1, 0, 0),
    c(1, 1, 0, 0),
    c(0, 0, 1, 1),
    c(0, 0, 1, 1)
  ),
  nrow = 4
)
dynet::single_unbiased_random_walker(input, 4)
dynet::single_unbiased_random_walker(input, 5, 2)
```

# Voter #
Simulate voter-model-style dynamics on a network.
        Nodes are randomly assigned a state in ${-1, 1}$; at each
        time step all nodes asynchronously update by choosing their new
        state uniformly from their neighbors. Generates an $N\times L$ time series.
        The results dictionary also stores the ground truth network as
        `'ground_truth'`.

## Params ##
#' @param noise if noise is present, with this probability a node's state will be randomly redrawn from (-1,1) \cr
#' independent of its neighbors' states. If 'automatic', set noise to 1/N.
#' @return results a list with TS matrix an N*L array of synthetic time series data.


* **input_matrix** The input (ground-truth) adjacency matrix of a graph with $N$ nodes. Must be valid square adjacency matrix.
* **L** Integer length of the desired time series.
* **noise** If noise is present, with this probability a node's state will be randomly redrawn from $(-1,1)$ independent of its neighbors' states. If omitted,  set noise to $1/N$.

## Returns ##
* An $N\times L$ matrix of synthetic time series data.
    
## Code Example ##
```{r}
input <- matrix(
  cbind(
    c(1.0, 1.0, 2.0, 3.0),
    c(0.0, 0.0, 1.0, 0.0),
    c(0.0, 0.0, 0.0, 1.0),
    c(0.0, 0.0, 0.0, 0.0)
  ),
  nrow = 4
)
dynet::voter(input, 5, .5)
dynet::voter(input, 10)
```